A geographic routing approach for IPv6 in large-scale low-power and lossy networks\tnoteref{note}

### 2015-05-04 2014_ELSEVIER_CEE_SI/paper_cee_special_issue.tex
added preprint note

\title{A geographic routing approach for IPv6 in large-scale low-power and lossy networks}

>>>>

\title{A geographic routing approach for IPv6 in large-scale low-power and lossy networks\tnoteref{note}}
\tnotetext[note]
{
This manuscript has been accepted for publication in Computers and Electrical Engineering. The manuscript will undergo copyediting, typesetting, and review of the resulting proof before it is published in its final form. Please note that during the production process errors may be discovered which could affect the content, and all disclaimers that apply to the journal apply to this manuscript. A definitive version was subsequently published in PUBLICATION, [VOL, ISSUE, (DATE)] DOI
}
